\addcontentsline{toc}{chapter}{Literatura} % SEM NESAHEJTE!
\begin{thebibliography}{99}   
% OBECNÉ PCG
	\bibitem{PCGinG}
    SHAKER, Noor; TOGELIUS, Julian a NELSON, Mark J. \textit{Procedural Content Generation in Games}. Switzerland: Springer International Publishing, 2016. ISBN 978-3-319-42714-0.
%file:///C:/Users/stepa/Downloads/978-3-319-42716-4%20(1).pdf

    \bibitem{HistoryOfPCG}
    SMITH, Gillian. \textit{An Analog History of Procedural Content Generation}. Paper. 360 Huntington Ave, 100 ME Boston, MA 02115, USA: Northeastern University, 2015.
%http://www.fdg2015.org/papers/fdg2015_paper_19.pdf

    \bibitem{PCGclanek}
    ANTONIOS LIAPIS. \textit{Constructive Generation Methods for Dungeons and Levels}. Online. Antoniosliapis.com. 2017. Dostupné z: \url{https://antoniosliapis.com/articles/pcgbook\_dungeons.php}. [cit. 2025-01-13].
%--------------------------------------------------

    \bibitem{BSPclanek}
    GEEKS FOR GEEKS. \textit{Binary Space Partitioning}. Online. Www.geeksforgeeks.org. 2020, 30 Sep, 2020. Dostupné z: \url{https://www.geeksforgeeks.org/binary-space-partitioning/}. [cit. 2025-01-13].

%--------------------------------------------------
% Agent-based

    \bibitem{Agent-basedClanek}
    DORAN, Jonathon a PARBERRY, Ian. Controlled Procedural Terrain Generation Using Software Agents. \textit{ReasearchGate}. 2010, vol.~2, no. 2, s.~111 - 119.
    %https://www.researchgate.net/publication/224133576_Controlled_Procedural_Terrain_Generation_Using_Software_Agents
%--------------------------------------------------
% Grammars
    %https://essay.utwente.nl/87002/
    \bibitem{GramClanek}
    \textit{Procedural Location Generation with Weighted Attribute Grammars}. Bakalářská práce. University of Twente P.O. Box 217, 7500AE Enschede The Netherlands: University of Twente, 2021.

    \bibitem{GramFand}
    \textit{Generative Grammars}. Online. Fandom.com. 2016. Dostupné z: \url{https://procedural-content-generation.fandom.com/wiki/Generative\_Grammars}. [cit. 2025-01-15].
%--------------------------------------------------
% Šum
    \bibitem{NoiseClanek}
    Travall. \textit{Procedural 2D Island Generation - Noise Functions}. Online. Https://medium.com. 2018. Dostupné z: \url{https://medium.com/@travall/procedural-2d-island-generation-noise-functions-13976bddeaf9}. [cit. 2025-01-16].

    \bibitem{perlinClanek}
    \textit{Perlin Noise}. Online. Scratchapixel.com. 2022. Dostupné z: \url{https://www.scratchapixel.com/lessons/procedural-generation-virtual-worlds/perlin-noise-part-2/perlin-noise.html}. [cit. 2025-01-16].

    %https://procedural-content-generation.fandom.com/wiki/Procedural_Content_Generation_Wiki
%--------------------------------------------------

    \bibitem{fracMath}
    BROWN, Adam. \textit{The Maths of Fractal Landscapes and Procedural Landscape Generation}. Online. Fractal-landscapes.co.uk. 2002 - 2020. Dostupné z: \url{https://www.fractal-landscapes.co.uk/maths.html}. [cit. 2025-01-16].

    \bibitem{waveClanek}
    HEATON, Robert. \textit{The Wavefunction Collapse Algorithm explained very clearly}. Online. Robertheaton.com. 17 Dec 2018. Dostupné z: \url{https://robertheaton.com/2018/12/17/wavefunction-collapse-algorithm/}. [cit. 2025-01-16].

    \bibitem{GANclanek}
    SPICK, Ryan J.; COWLING, Peter a WALKER, James Alfred. \textit{Procedural Generation using Spatial GANs for Region-Specific Learning of Elevation Data}. Paper. University of York, UK: University of York, 2019.


    
\end{thebibliography}